\documentclass[text.tex]{subfiles}

\begin{document}
\begin{thebibliography}{9}

\bibitem{nobel}
\emph{The Nobel Prize in Chemistry 2011 - Popular Information}. Nobelprize.org. Nobel Media AB 2014. Web. 3 May 2017. \url{http://www.nobelprize.org/nobel_prizes/chemistry/laureates/2011/popular.html}

\bibitem{lagarias}
J~C~LAGARIAS. \emph{Geometric Models for Quasicrystals I. Delone Sets of Finite Type.} Discrete \& Computational Geometry 21.2 (1999): 161-91. Web.

\bibitem{number}
Z~MASÁKOVÁ, E~PELANTOVÁ. \emph{Teorie čísel}. V Praze: České vysoké učení technické v Praze, 2017. 178 stran. ISBN 978-80-01-06030-8.

\bibitem{distances}
Z~MASÁKOVÁ, J~PATERA, E PELANTOVÁ. \emph{Lattice-like properties of quasicrystal models with quadratic irrationalities},  Proceedings of Quantum Theory and Symmetries, Goslar, 1999, Eds. H.D. Doebner, V.K. Dobrev, J.D. Hennig, W. Luecke, World Scientific, 2000, pp. 499-509.

\bibitem{classification}
	Z~MASÁKOVÁ, J PATERA, J ZICH. \emph{Classification of Voronoi and Delone tiles in quasicrystals: I. General method.} J. Phys. A \textbf{36} (2003), 1869--1894.

\bibitem{classificationII}
	Z~MASÁKOVÁ, J PATERA, J ZICH. \emph{Classification of Voronoi and Delone tiles of quasicrystals: II. Circular acceptance window of arbitrary size.} J. Phys. A \textbf{36} (2003), 1895--1912.

\bibitem{classificationIII}
	Z~MASÁKOVÁ, J PATERA, J ZICH. \emph{Classification of Voronoi and Delone tiles of quasicrystals: III. Decagonal acceptance window of any size.} J. Phys. A \textbf{38} (2005), 1947--1960.

\bibitem{combinatorial}
	L-S GUIMOND, Z~MASÁKOVÁ, E PELANTOVÁ. \emph{Combinatorial properties of infinite words associated with cut-and-project
 sequences.} J. Théor. Nombres Bordeaux \textbf{15} (2003), 697--725.
	
\bibitem{magister}
	J ZICH. \emph{Voronoi \& Delone tiling of quasicrystals}. Fakulta jaderná a fyzikálně inženýrská České vysoké učení technické v~Praze, 2002. Diplomová práce. Vedoucí práce Z~Masáková.

\section*{Mentions}
\bibitem{mention01}
\uppercase{P.~H. Chen, K.~Avchachov, K.~Nordlund, K.~Pussi.} 
\emph {Molecular dynamics simulation of radiation damage in CaCd6 quasicrystal cubic approximant up to 10 keV}. {Journal of Chemical Physics}, {138}({23}), {2013}.

\bibitem{mention02}
\uppercase{S.~Deloudi, W.~Steurer.} 
\emph {Higher-dimensional crystallography of N-fold quasiperiodic tilings}. {Acta Crystallographica Section A}, {68}({2}):{266--277}, {2012}.

\bibitem{mention03}
\uppercase{S.~Katrych, Th. Weber, A.~Kobas, L.~Massueger, L.~Palatinus, G.~Chapuis, W.~Steurer.} 
\emph {New stable decagonal quasicrystal in the system Al-Ir-Os}. {Journal of Alloys and Compounds}, {428}({1-2}):{164--172}, {2007}.

\bibitem{mention04}
\uppercase{D.~Logvinovich, A.~Simonov, W.~Steurer.} 
\emph {Structure of decagonal Al-Ni-Rh}. {Acta Crystallographica Section B}, {70}({4}):{732--742}, {2014}.
	
\end{thebibliography}
\end{document}

